Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-06 paper/structureScene.tex
relevance based quantization is now in the manuscript

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
%\title{An evaluation framework for event detection using a morphological model of acoustic scenes}
\title{Auditory Scene Similarity Retrieval and Classification with Wavelet Scattering}

@@

This paper introduces a generic hierarchical modeling scheme for acoustic scenes using the wavelet scattering transform at sub-second timescales with object-based segmentation at larger timescales. Applying the proposed approach to the acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets using a state-of-the-art classifier demonstrates the potential of the features designed using the wavelet scattering transform, consistently outperforming a baseline of mel-frequency cepstral coefficients (MFCCs).

In addition, representing the scene at larger time scale as a set of representative features from coherent segments is an effective approach for acoustic scene similarity retrieval, because it allows the retrieval system to focus on discriminative features.
\end{abstract}

@@

The work described in this paper attempts to answer this question by demonstrating the usefulness of two concepts: 1) using the wavelet scattering transform to extract discriminative features subject to a small number of parameters and 2) object-based modeling of the acoustic scene based on unsupervised clustering of each acoustic scene, allowing us to focus the scene description on a few salient sound objects that carry most of the semantic information.

@@

\section{Object-based modeling of the scene}
\label{sec:object}

@@

\subsubsection*{Object-based \vs early integration}

For the scattering transform, both \emph{ob-c} and \emph{ob-w} outperform \emph{early}, thus confirming the benefits of using an object-based representation to refine the similarity measures between the scenes. However, it is worth noticing that \emph{ob-a} performs comparably to \emph{early}, showing that the discriminant information is destroyed by averaging the contributions from all centroids. To take advantage of an object-based representation, we need to select certain representative centroids when comparing objects. Furthermore, it appears that \emph{ob-c} is better able to characterize the classes than \emph{ob-w}. This last observation suggests that weighting a centroid according to the number of frames it contains may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may shared a lot of similar sound sources with only a few sources discriminating between them.

@@

Surprisingly, although we ran a large number of experiments to formulate object-based clustering into a supervised setting for acoustic scene classification, none managed to outperform the baseline strategy in temporal integration, namely majority voting. Among object-based methods, the best result is achieved by the \emph{ob-c} approach with log-compressed scattering coefficients, reaching an accuracy of $66\% \pm0.7$. This might be due to the fact that the discriminability gained by the object-based approach is already gained by the classifiers during the training and the fact the object-based approach is equivalent to an early fusion approach, which in the case of the DCASE 2013 has not been identified as beneficial due to the dataset size (see discussion in Section \ref{sec:eili}).

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
%\title{An evaluation framework for event detection using a morphological model of acoustic scenes}
\title{Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features}

@@

This paper introduces a generic hierarchical modeling scheme for acoustic scenes using the wavelet scattering transform at sub-second timescales with relevance based quantization at larger timescales. Applying the proposed approach to the acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets using a state-of-the-art classifier demonstrates the potential of the features designed using the wavelet scattering transform, consistently outperforming a baseline of mel-frequency cepstral coefficients (MFCCs).

In addition, representing the scene at larger time scale as a set of representative features from coherent segments is an effective approach for acoustic scene similarity retrieval, as it is found that it allows the retrieval system to focus on discriminative features.
\end{abstract}

@@

The work described in this paper attempts to answer this question by demonstrating the usefulness of two concepts: 1) using the wavelet scattering transform to extract discriminative features subject to a small number of parameters and 2) large time scale modeling of the acoustic scene based on unsupervised clustering of each acoustic scene, allowing us to hopefully focus the scene description on a few salient sound objects that carry most of the semantic information.

@@

\section{Relevance based quantization of features}
\label{sec:object}

@@

\subsubsection*{Relevance-based quantization \vs early integration}

For the scattering transform, both \emph{ob-c} and \emph{ob-w} outperform \emph{early}, thus confirming the benefits of using an relevance-based quantization to improve the similarity measures between the scenes. However, it is worth noticing that \emph{ob-a} performs comparably to \emph{early}, showing that the discriminant information is destroyed by averaging the contributions from all centroids. To take advantage of an such a representation, we need to select certain representative centroids when comparing quantized objects. Furthermore, it appears that \emph{ob-c} is better able to characterize the classes than \emph{ob-w}. This last observation suggests that weighting a centroid according to the number of frames it contains may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may shared a lot of similar sound sources with only a few sources discriminating between them.

@@

Surprisingly, although we ran a large number of experiments to formulate the relevance-based quantization scheme into a supervised setting for acoustic scene classification, none managed to outperform the baseline strategy in temporal integration, namely majority voting. Among such methods, the best result is achieved by the \emph{ob-c} approach with log-compressed scattering coefficients, reaching an accuracy of $66\% \pm0.7$. This might be due to the fact that the discriminability gained by the relevance-based quantization approach is already gained by the classifiers during the training and the fact the relevance-based quantization approach is equivalent to an early fusion approach, which in the case of the DCASE 2013 has not been identified as beneficial due to the dataset size (see discussion in Section \ref{sec:eili}).
